%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% phys.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Many years of experience with Geant4 across a large number of applications 
%has demonstrated the significant advantage of a modular physics lists approach, 
%where each type of physics is instantiated by a \emph{physics constructor} 
%class. Geant4 maintains several EM constructors (Table~\ref{em:physl}) which 
%are created for different application domains. These constructor classes are 
%components of full Geant4 reference physics lists 
%(for example, $FTFP\_BERT$, $FTFP\_BIC\_EMY$...), and are available for EM 
%production physics constructors (names are defined in Table~\ref{em:physl}). 
%At the same time, all EM constructors may be directly used by custom 
%physics lists.

%The physics of a \Gfour\ simulation is built in a modular approach, in which a
%list (called a physics list) of interaction types is created. 

Electromagnetic physics is defined in physics constructor classes, which are
components of full physics classes. \Gfour{} maintains several EM constructors
(Table~\ref{em:physl}) for different application domains. The constructors are 
used by both \Gfour{} reference physics lists and custom physics lists.

For HEP experiments, high efficiency CPU performance is required, and, as 
such, the HEP physics configuration should provide a compromise between 
accuracy and CPU speed. For simulation of shielding in space and for radiation 
dose in medical studies, more detailed tracking of low energy particles is 
required. For this purpose, in physics constructors oriented towards medicine 
and space science applications 
(i.e. \gclass{G4EmStandardPhysics\_option4}, named $EMZ$), more strong step 
limitation are defined and models with more detailed treatment of atomic 
effects and detailed ion stopping powers are applied. A general goal is to 
provide a physics constructor with set of the most accurate models for each 
energy range and particle type.

To assist in the production and testing of physics constructors, 
experimental constructors are available. 
\Gfour{}-DNA physics constructors are applicable only 
for a limited set of materials (mainly liquid water). Examples 
of how to build physics lists with \Gfour{}-DNA physics, low energy, 
and standard 
physics \cite{embib:uni} are distributed with \Gfour{}. Specific physics 
constructors are provided for optical physics which can be added 
on top of any existing physics list.

\begin{table*}
\caption{List of \Gfour{} EM physics constructors}
\label{em:physl}
\begin{center}
\begin{tabular}{llll}
\hline
Constructor& Application& Name & Comment \\ \hline
\gclass{G4EmStandardPhysics} & HEP &  &default (ATLAS)\\
\gclass{G4EmStandardPhysics_option1} & & EMV & simplified (CMS)\\
\gclass{G4EmStandardPhysics_option2} & & EMX & simplified (LHCb)\\
\hline
\gclass{G4EmStandardPhysics_option3} & space \& & EMY & detailed  \\
                             &  medicine &     & standard models\\
\gclass{G4EmLivermorePhysics} & & LIV & detailed  \\
                     &       &          &  Livermore models\\
\gclass{G4EmPenelopePhysics} &  & PEN & detailed \\ 
                    &  &     & Penelope models\\
\gclass{G4EmStandardPhysics_option4} &  & EMZ & combining \\
                             &  &     & best models\\
\hline
\gclass{G4EmLivermorePolarizedPhysics} &  &  & polarized models\\
\gclass{G4EmLowEPPhysics} &  &  & new low energy models\\
\gclass{G4EmStandardPhysicsWVI} &  &  & WVI multiple scattering\\
\gclass{G4EmStandardPhysicsSS} &  &  & single scattering \\
\hline
\gclass{G4EmDNAPhysics} & DNA &  & default for DNA physics \\
\gclass{G4EmDNAPhysics_option1} & DNA &  & WVI multiple scattering \\
\hline
\gclass{G4OpticalPhysics} & all &  & production and transport \\
                 &     &  & of optical photons \\
\hline
\end{tabular}
\end{center}
\end{table*}
