%
% References to hadronic section of GP2014
%
\bibitem{hadbib:bar90} V.S Barashenkov, Pion-nucleus cross-sections,
                       Preprint P2-90-158, Dubna 1990.

\bibitem{hadbib:bar89} V.S Barashenkov, Nucleon-nucleus cross-sections,
                       Preprint P2-89-770, Dubna 1989.

\bibitem{hadbib:ggepjc} V.M. Grichine, European Physical Journal C 62 (2009) 399.
% 399-404.

\bibitem{hadbib:ggnimb} V.M. Grichine,
                        Nuclear Instruments and Methods in Physics Research B 267 (2009) 2460.
% 2460-2462.

\bibitem{hadbib:PDG} Particle Data Group, \url{http://pdg.lbl.gov/2006/reviews/hadronicrpp.pdf} .

\bibitem{hadbib:ihepbase} Institute for High Energy Physics database, Protvino, Russia,
                          \url{http://wwwppds.ihep.su} .

\bibitem{hadbib:dubnabase} Nuclear Energy Agency, France,
                           \url{http://www.nea.fr/html/dbdata/bara.html} .

\bibitem{hadbib:CHIPS} M.V. Kossov, European Physical Journal A 14 (2002) 265; \\
                       P.V. Degtyarenko, M.V. Kossov and H.P. Wellisch,
                         European Physical Journal A 8 (2000) 217; \\
                       P.V. Degtyarenko, M.V. Kossov and H.P. Wellisch,
                         European Physical Journal A 9 (2000) 411; \\
                       P.V. Degtyarenko, M.V. Kossov and H.P. Wellisch,
                         European Physical Journal A 9 (2000) 421.

% AntiNucleus-Nucleus ------------------------
\bibitem{hadbib:AntiA1} V. Franco and R.J. Glauber,
                        Physical Review 142 (1966) 1195.

\bibitem{hadbib:AntiA2} V. Franco, Physical Review 175 (1968) 1376.

\bibitem{hadbib:AntiA3} O.D. Dalkarov and V.A. Karmanov,
                        Nuclear Physics A 445 (1985) 579.

\bibitem{hadbib:AntiA4} A.M. Zadorozhnyi, V.V. Uzhinsky and S.Yu. Shmakov,
                        Soviet Journal of Nuclear Physics 39 (1984) 729; \\
                        Yadernaya Fizika 39 (1984) 1155.

\bibitem{hadbib:AntiA5} S.Yu. Shmakov, V.V. Uzhinskii and A.M. Zadorozhny,
                       Computer Physics Communications 54 (1989) 125.

\bibitem{hadbib:AntiA6} W. Broniowski, M. Rybczynski and P. Bozek,
                        Computer Physics Communications 180 (2009) 69.

\bibitem{hadbib:AntiA7} V. Uzhinsky, J. Apostolakis, A. Galoyan, G. Folger, V.M. Grichine,
                        V.N. Ivanchenko and D.H. Wright,
                        Physics Letters B 705 (2011) 235.

\bibitem{hadbib:AntiA8} S.P. Denisov et al.,
                        Nuclear Physics B 31 (1971) 253.

\bibitem{hadbib:AAx4} P. Shukla, Physical Review C 67 (2003) 054607.

\bibitem{hadbib:AAx5} H.L. Bradt and B. Peters, Physical Review 77 (1950) 54.

\bibitem{hadbib:AAx6} S. Barshay, C.B. Dover and J.P. Vary,
                      Physics Letters 51B (1974) 5; \\
                      Physical Review C 11 (1975) 360.

\bibitem{hadbib:AAx7} L. Sihver, C.H. Tsao, R. Silberberg, T. Kanai and A.F. Barghouty,
                      Physical Review C 47 (1993) 1225.

\bibitem{hadbib:AAx8} S. Kox et al., Physical Review C 35 (1987) 1678.

\bibitem{hadbib:AAx9} W.-Q. Shen, B. Wang, J. Feng, W.L. Zhan, Y.T. Zhu and E.P. Feng,
                      Nuclear Physics A 491 (1989) 130.

% String models
\bibitem{hadbib:FTF1} A. Capella, U. Sukhatme, C.I. Tan and J. Tran Thanh Van,
                      Physics Reports 236 (1994) 227.

\bibitem{hadbib:FTF2} A.B. Kaidalov, Physics Letters 116 B (1982) 459; \\
                     A.B. Kaidalov and K.A. Ter-Martirosyan
                     Physics Letters 117 B (1982) 247.

\bibitem{hadbib:FTF3} B. Andersson, G. Gustafson and B. Nilsson-Almqvist,
                      Nuclear Physics B 281 (1987) 289.

\bibitem{hadbib:FTF4} B. Nilsson-Almqvist and E. Stenlund,
                      Computer Physics Communications 43 (1987) 387.

\bibitem{hadbib:FTF19} Geant4 Collaboration, Geant4 Physics Reference Manual,
    \url{http://geant4.web.cern.ch/geant4/UserDocumentation/UsersGuides/PhysicsReferenceManual/fo/PhysicsReferenceManual.pdf}

\bibitem{hadbib:FTF7} B. Andersson, G. Gustafson, G. Ingelman and T. Sj$\ddot{o}$strand,
                      Physics Reports 97 (1983) 31.

\bibitem{hadbib:Alvi} M. Alvioli and M. Strikman, Physics Letters B722 (2013) 347.

\bibitem{hadbib:FTF18} K.G. Boreskov, A.B. Kaidalov, S.M. Kiselev and
                       N.Ya. Smorodinskaya, Yadernaya Fizika 53 (1991) 569.

\bibitem{hadbib:FTF10} Kh. Abdel-Waged, N. Felemban and V.V. Uzhinskii,
                       Physical Review C 84 (2011) 014905.

\bibitem{hadbib:FTF8} Kh. Abdel-Waged and V.V. Uzhinsky,
                      Physics of Atomic Nuclei 60 (1997) 828 (Yadernaya Fizika 60 (1997) 925).\\
                      Kh. Abdel-Waged and V.V. Uzhinsky, Journal of Physics G 24 (1997) 1723.

\bibitem{hadbib:FTF9} M.I. Adamovich et al. (EMU-01 Collaboration),
                      Zeitschrift fur Physik A 358 (1997) 337.

\bibitem{hadbib:FTF11} A.Y. Abul-Magd, W.A.Friedman and J.Hufner,
                       Physical Review C 34 (1986) 113.

\bibitem{hadbib:FTF12} G. Folger, V.N. Ivanchenko and J.P. Wellisch,
                       European Physical Journal A 21 (2004) 407.

\bibitem{hadbib:FTF16} V.A. Abramovsky, V.N. Gribov and O.V. Kancheli,
                       Yadernaya Fizika 18 (1973) 595
                       (Soviet Journal of Nuclear Physics 18 (1974) 308).

\bibitem{hadbib:FTF17} A. Bolshakova et al. (HARP-CDP Group),
                       European Physical Journal C 70 (2010) 543.

% Cascades
\bibitem{hadbib:bert} D.H. Wright and M.H. Kelsey, Nuclear Instruments and Methods
                      in Physics Research A 804 (2015) 175.

\bibitem{hadbib:binary} G. Folger, V. Ivanchenko and H.-P. Wellisch,
                        European Physical Journal A 21 (2004) 404.

\bibitem{hadbib:incl} A. Boudard, J. Cugnon, J.-C. David, S. Leray and D. Mancusi,
                      Physical Review C 87 (2013) 014606.

\bibitem{hadbib:inclxx} D. Mancusi, A. Boudard, J. Cugnon, J.-C. David,
                        P. Kaitaniemi and S. Leray,
                        Physical Review C 90 (2014) 054602.

\bibitem{hadbib:ablav3} J.-J. Gaimard and K.-H. Schmidt,
                        Nuclear Physics A 531 (1991) 709; \\
                        J. Benlliure, A. Grewe, M. de Jong, K.-H. Schmidt and
                        S. Zhdanov,
                        Nuclear Physics A 628 (1998) 458.

% Precompound
\bibitem{hadbib:gudima83} K. ~Gudima, S.~G.~Mashnik and V. D. Toneev,
                          Nuclear Physics A 401 (1983) 329.

\bibitem{hadbib:calor-2008} John Apostolakis et al.
% Gunter Folger, Vladimir Grichine,
%  Aatos Heikkinen, Alex Howard, Vladimir Ivanchenko, Pekka Kaitaniemi,
%  Tatsumi Koi, Mikhail Kosov, Jose Manuel Quesada, Alberto Ribon,
%  Vladimir Uzhinski, Dennis Wright,
                            Journal of Physics: Conference Series 160 (2009) 012073.
  Proceedings of the XIII International Conference on Calorimetry in High Energy
  Physics (CALOR 2008), Pav\'{\i}a, Italy, May 26-30, 2008.

\bibitem{hadbib:ijrb-space-2012} A. Ivanchenko, V. Ivanchenko, J.M. Quesada and S. Incerti,
                                 International Journal of Radiation Biology 88 (2012) 171.

\bibitem{hadbib:iaea-spa-2009} J. M. Quesada, Proceedings of the International Topical Meeting on
                               Nuclear Research Applications and Utilization of Accelerators.
                               Satellite Meeting on Spallation Reactions, Viena, Austria, May 4-8, 2009.

% Deexcitation
\bibitem{hadbib:mfm-bondorf-1995} J.P. Bondorf, A.S. Botvina, A.S. Iljinov, I.N. Mishustin,
                                  K. Sneppen,
                                  Physics Reports 257 (1995) 133.
% 133-221.

\bibitem{hadbib:jinr-fis-1977} V.S. Barashenkov et al.,
                               Communications JINR, P4-10781, Dubna 1977.

\bibitem{hadbib:inr-fis-1993} G.D. Adeev et al.,
                              Preprint INR 816/93 Moscow (1993) (in Russian).

\bibitem{hadbib:weisskopf-1940} V. ~E.~Weisskopf and D.~H.~Ewing,
                                Physical Review 57 (1940) 472.

\bibitem{hadbib:gem-2001} S. Furihata, K. Niita, S. Meigo, Y. Ikeda and
                          F. Maekawa,
                          JAERI-Data/Code 2001-015, Japan Atomic Energy Research Institute (2001).

\bibitem{hadbib:ENSDF} National Nuclear Data Center,
                       Evaluated Nuclear Structure Data Files,
                       \url{http://www.nndc.bnl.gov/ensdf} .

\bibitem{hadbib:pmb-fluka-g4-2011} T.T. B\"{o}hlen, F. Cerutti, M. Dosanjh, A. Ferrari, I. Gudowska,
                                   A. Mairani and J.M. Quesada,
                                   Physics in Medicine and Biology 55 (2010) 5833.
% 5833-5847.

\bibitem{hadbib-iaea-spa-benchmark} S. Leray et al.,
                                    Journal of the Korean Physical Society 59 (2011) 791.

\bibitem{hadbib:pnst-preco-2011} J. M. Quesada, V. Ivanchenko, A. Ivanchenko,
                                 M. A. Cort\'es-Giraldo, G. Folger, A. Howard and D.H. Wright,
% on behalf of the Geant4 Hadronic Working Group,
  Progress in Nuclear Science and Technology 2, (2011) 936.
  Proceedings of the Joint International Conference on Supercomputing in Nuclear
  Applications and Monte Carlo 2010 (SNA+MC2010) Tokyo, Japan, October 2010.

\bibitem{hadbib:nima-pshenich-2010} I. Pshenichnov, A. Botvina, I. Mishustin
                                    and W. Greiner,
                                    Nuclear Instruments and Methods in Physics Research B 268 (2010) 604.
% 604-615.

\bibitem{hadbib:prompt-gamma-2014} G. Dedes, M. Pinto, D. Dauvergne, N. Freud, J. Krimmer,
                                   J. M. Letang, C. Ray and E. Testa,
                                   Physics in Medicine and Biology 59 (2014) 1747.


% Elastic
\bibitem{hadbib:gheisha} H.C. Fesefeldt, Simulation of hadronic showers, physics and application,
                         Technical Report PITHA 85-02 (1985).

\bibitem{hadbib:glauber70} R.J. Glauber, in ``High Energy Physics and Nuclear
                           Structure'', edited by S. Devons, Plenum Press,
                           New York, 1970.

\bibitem{hadbib:difel} V.M. Grichine, Computer Physics Communications 181 (2010) 921.
% 921-927.

\bibitem{hadbib:alkh78} G.D. Alkhazov, S.L. Belostotsky and A.A. Vorobyov,
                        Physics Reports 42 (1978) 89.


% Neutrons
\bibitem{hadbib:ENDF} M.B. Chadwick et al.,
%                      "ENDF/B-VII.1 Nuclear Data for Science and Technology:
%                       Cross Sections, Covariances, Fission Product Yields
%                       and Decay Data", 
                      Nuclear Data Sheets 112, 2887 (2011).

\bibitem{hadbib:BROND} H.D. Lemmel and P.K. McLaughlin, ``BROND-2.1 Russian Evaluated
                       Neutron Data Library'', IAEA-NDS-90, Rev. 7, 1993.

\bibitem{hadbib:CENDL} L. Tingjin, L. Qichang and S. Zongdi, 
%                        ``CENDL-2, Chinese Evaluated Nuclear Data Library, Version 2'',
                       Nuclear Data for Science and Technology, 
                       Research Reports in Physics (1992) 804.

\bibitem{hadbib:EFF} H.D. Lemmel, EFF-2.4, The European Fusion File 1994,
                     including revisions up to May 1995, 
                     Summary Documentation, IAEA-NDS-170, June 1995.
% M.E. Kellet, R.A. Forrest and P. Batistoni, 
%                      A brief overview of the European Fusion File project,
%                      19th International Conference on Fusion Energy 2002, Lyon, France, 
%                      October 2002.

\bibitem{hadbib:FENDL} A.B. Pashchenko, H. Wienke and S. Ganesan,
%                       "FENDL: International reference nuclear data library
%                        for fusion applications",
                        Journal of Nuclear Materials Volumes 233-237, 1601 (1996).

\bibitem{hadbib:JEF} C. Nordborg and M. Salvatores,
                     Status of the JEF Evaluated Data Library,
                     Proceedings of the International Conference on Nuclear Data for
                     Science and Technology, Gatlinburg, Tennessee, USA, May 1994, 
                     2, 680. 

\bibitem{hadbib:JENDLFF} S. Chiba et al.,
                        Journal of Nuclear Science and Technology 39 (2002) 187.

\bibitem{hadbib:JENDL3} T. Nakagawa et al., 
                        Journal of Nuclear Science and Technology 32 (1995) 1259.

\bibitem{hadbib:MENDL} Yu.N. Shubin et al., MENDL-2 Neutron reaction data library 
                       for nuclear activation and transmutation at intermediate 
                       energies, IAEA-NDS-136, 1995. 

\bibitem{hadbib:mendoza} E. Mendoza, D. Cano-Ott, T. Koi and C. Guerrero,
%                         "New standard evaluated neutron cross section libraries
%                         for the GEANT4 code and first verification",
                         IEEE Transactions on Nuclear Science 61 (2014) 2357.

\bibitem{hadbib:IAEA} International Atomic Energy Agency Nuclear Data Services,
                      \url{https://www-nds.iaea.org/geant4/} .

\bibitem{hadbib:llnlftp} Lawrence Livermore National Laboratory General Nuclear Data,
                         \url{ftp://gdo-nuclear.ucllnl.org/pub} .

% Nucleus-Nucleus Xs  ------------------------
\bibitem{hadbib:wilson} J.W. Wilson et al., NUCFRG2: An Evaluation of the
                       Semi-empirical Nuclear Fragmentation Database, NASA
                       Technical Report 3533, 1995.


%% Radioactive decay
% \bibitem{hadbib:ENSDF} National Nuclear Data Center,
%                       Evaluated Nuclear Structure Data Files,
%                       \url{http://www.nndc.bnl.gov/ensdf} .

% \bibitem{hadbib:AAx1} J.D.~Jackson,
%   Classical Electrodynamics, 2nd ed., Wiley, New York, 1975.

% \bibitem{hadbib:AAx2} C.A.~Bertulani and G.~Baur, Physics Reports 163 (1988) 299.

% \bibitem{hadbib:AAx3} I.A.~Pshenichnov, I.N.~Mishustin, J.P.~Bondorf,
%                       A.S.~Botvina and A.S.~Iljinov, Physical Review C 60 (1999) 044901; \\
%                       I.A.~Pshenichnov, J.P.~Bondorf, I.N.~Mishustin, A.~Ventura,
%                       and S.~Masetti, Physical Review C 64 (2001) 024903.

% \bibitem{hadbib:AAx10} V. Uzhinsky, arXiv:1209.4455 [nucl-ex], (2012).

% \bibitem{hadbib:FTF13} S.A. Bass et al.,
%                        Progress in Particle and Nuclear Physics 41 (1998) 255; \\
%                        M. Bleicher et al., Journal of Physics G 25 (1999) 1859.

% \bibitem{hadbib:FTF14} X.-N. Wang and M. Gyulassy,
%                        Physical Review D 44 (1991) 3501. \\
%                        M. Gyulassy and X.-N. Wang,
%                        Computer Physics Communications 83 (1994) 307.

% \bibitem{hadbib:FTF15} H. Pi, Computer Physics Communications 71 (1992) 173.

% PRECO -DE-EX ------------------------------------------------------------
% JMQ 

% \bibitem{hadbib:griffin66} J. ~J.~Griffin,
%                            Physical Review Letters 17 (1966) 478.

% \bibitem{hadbib:chep-2010a} Geant4 Hadronic Working Group,
%                             Journal of Physics: Conference Series 331 (2011) 032002.
%   Proceedings of the International Conference on Computing in High Energy and
%   Nuclear Physics (CHEP 2010) Taipei, Taiwan, November 2010.

% \bibitem{hadbib:chep-2010b} S. Banerjee et al.,
%  G. Folger, A. Ivanchenko,
%   V. N. Ivanchenko, M. Kossov, J. M. Quesada, A. Schälicke, V. Uzhinsky,
%   H. Wenzel, D. H. Wright and J. Yarba,
%                            Journal of Physics: Conference Series 331 (2011) 032034.
%  Proceedings of the International Conference on Computing in High Energy and
%  Nuclear Physics (CHEP 2010) Taipei, Taiwan, November 2010.

% \bibitem{hadbib:mc2010} D.H. Wright,
% on behalf of the Geant4 Hadronic Working Group,
%                         Proceedings of the Joint International Conference on 
%                         Supercomputing in Nuclear Applications and Monte Carlo
%                         2010 (SNA+MC2010) Tokyo, Japan, October 2010.

% \bibitem{hadbib-iaea-spa-benchmark} S. Leray et al.,
%                                    Journal of the Korean Physical Society 59 (2011) 791.


