
\subsection{\textbf{Hadronic physics}}\label{sec:hadphys}
\Gfour{} hadronic physics is loosely defined to cover any reaction which can
produce hadrons in its final state.  As such, it covers purely hadronic
interactions, lepton- and gamma-induced nuclear reactions, and radioactive
decay.  The interaction is represented as a \Gfour{} process which consists of
a cross section to determine when the interaction will occur, and a model which
determines the final state of the interaction.    

Models and cross sections are provided which span an energy range from sub-eV to
~TeV.  Following the toolkit philosophy, more than one model or process is 
usually offered in any given energy range in order to provide alternative 
approaches for different applications. 

During the last several years, new models and cross sections have been added
to the toolkit, while others have been improved and some obsolete models have
been removed.

% shortcut commands for some model names
\newcommand{\incl}{INCL}
\newcommand{\inclxx}{INCL++}
\newcommand{\abla}{ABLA~V3}

%------------------------ Uzhi part ----------------------------------
% A simulation of a particle propagation in a matter requires the following steps:
% a choice of an interaction point and a target nucleus which depend on cross sections
% of the particle interactions with components of the matter, a sampling of a reaction
% of the particle with chosen target nucleus and a simulation of the reaction.
%---------------- Uzhi changes -----------------------------------

\subsubsection{Hadronic cross sections}\label{sec:crosssections}
Total, inelastic and elastic cross sections for hadron-nucleus, nucleus-nucleus
and antinucleus-nucleus reactions are provided which cover energies up to ~TeV 
in some cases.  Proton-, neutron- and pion-nucleus cross sections at low to 
medium energies have been available in \Gfour{} since its beginning and their 
details are covered elsewhere \cite{bib:generalpaper2}.  The focus here is on 
recent developments in cross sections for other projectile types and at higher
energies. \\

% done
\input{hadronic/barashenkov.tex}

% done
\input{hadronic/glaubergribov.tex}

% done 
\input{hadronic/chipsextract.tex}

% done
\input{hadronic/antibaryonXS.tex}

% done
\input{hadronic/nucleusnucleusXS.tex}

\subsubsection{Hadronic models and processes}\label{sec:models}
Due to the large energy range covered, it is not possible for a single model to
describe all the physics encountered in a simulation.  A typical sequence of 
reactions may begin with a high energy hadron-nucleon collision within a nucleus
(QCD or parton string model), followed by the propagation of the secondaries of 
the collision through the nuclear medium (intra-nuclear cascade model), followed
by the de-excitation of the remnant nucleus (precompound model) and its 
evaporation of particles (evaporation and breakup models) until it reaches the 
ground state.  Each of these stages is qualitatively different from the other 
and will be discussed in turn, highlighting recent developments. 

Other reactions covered include nucleus-nucleus interactions (QMD or 
parton-based models), elastic models  (including coherent hadron scattering 
from nuclei), capture, and lepton- and gamma-nuclear interactions.

% Some of them are considered in
% Sec.~\ref{sec:models}. At low energy ($<$ 10 MeV) a negative charged or neutral
% particle can be absorbed by a target nucleus. A simulation of the reactions
% is presented in subsection~\ref{had:stopping}. At higher energies but below
% meson production threshold there can be only elastic hadron-nucleon scattering
% and potential interactions.
% Thus we have implemented in \Gfour three of
% such models -- BIN, QMD and \inclxx. The binary model (BIN) was described in
% \Gfour paper~\cite{G4}. Below a short description of the QMD model and
% the Li\`{e}ge Intranuclear Cascade model (\inclxx) will be presented
% \cite{hadbib:inclxx}.

\input{hadronic/string.tex}  \label{had:string}
\input{hadronic/cascade.tex} \label{had:cascade}
\input{hadronic/precompound.tex} 
\input{hadronic/deexcitation.tex} \label{had:deexcitation}

\input{hadronic/elastic.tex}

\input{hadronic/stopping.tex} \label{had:stopping}

% needs names of kinematic models 
\input{hadronic/neutrons.tex}

% \input{hadronic/cascade.tex} \label{had:cascade}

% \input{hadronic/string.tex}  \label{had:string}


%\subsubsection{Nuclear de-excitation model}
% \label{sec:evaporation}

% \input{hadronic/precompound.tex}

% \input{hadronic/deexcitation.tex} \label{had:deexcitation}

% needs discussion of G4NuclNuclDiffuseElastic
\input{hadronic/nucleusnucleus.tex}

\input{hadronic/radioactivedecay.tex}

\input{hadronic/gamleptnuclear.tex} \label{had:gamleptnucleus}

\input{hadronic/obsoletemodels.tex}


